TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-06 CORL/example.tex
Modified example.tex and added references

In this paper, we'll mostly focus on a dataset that involves three alphabet blocks that are moved across a table.
Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
This dataset is analogous to data that would be collected for a third-person robotic grasping task.
However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper. ((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).

@@

\section{Method}
\label{sec:text}

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/learnable_textures.pdf}
		\end{center}
		\caption{
			This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}.
		}
		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
		\label{fig:learnable_textures}
	\end{figure}

	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$. This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.

@@

@@

>>>>

In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
This dataset is analogous to data that would be collected for a third-person robotic grasping task.
However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper. ((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).

@@

\section{Method}
\label{sec:method}

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/learnable_textures.pdf}
		\end{center}
		\caption{
			This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's U and V axes using fourier feature networks.
		}
		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
		\label{fig:learnable_textures}
	\end{figure}

	$B$ is the batch size. Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$. This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.

@@

\subsection{Image Translation}
Our image translation module $T$ is based on the image translation module used in \citep{surgical_video_translation}, which is a variant of MUNIT \cite{munit}. Like in \citep{surgical_video_translation} but unlike MUNIT, however, the style code is fixed and noise is injected into the latent codes to prevent overfitting. During inference, our image translation module is completely determinstic.

$T$ is a bidirectional image translation module, and has two translation directions. $T_{A\rightarrow B}$ translates sim to real (aka domain A to domain B), and $T_{B\rightarrow A}$ translates real to sim (aka domain B to domain A). The simulation domain A (UVL maps concatenated to their texture projections) has 6 channels, whereas the real image domain B (photographs) has 3 channels.

Apart from these differences, the losses pertaining directly to image translation are the same as that in MUNIT.

Due to the way MUNIT works, we define
$T_{A\rightarrow B}\left(c\right) = dec_B\left(enc_A\left(c\right)\right)$
and 
$T_{B\rightarrow A}\left(p\right) = dec_A\left(enc_B\left(p\right)\right)$
where $enc_A, enc_B, dec_A, dec_B$ are encoders and decoders for domains A and B respectively, $p$ is a batch of real photos, and $c$ is a batch of simulated UVL+projection concatenations.

\subsection{Unprojection Consistency Loss}

@@

This benefits from large batch sizes, but that often makes you run out of vram.

Also, you have to get lucky - two scene pictures have to show the same side of a cube for example. First person scenarios would be even worse.

Also, the resolution of the unprojection matters:

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
	\end{center}
	\caption{
		The resolution of an unprojection matters for unprojection consistency loss. The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, lowering numerical instability.
	}
	\label{fig:unprojection_resolution_comparison}
\end{figure}

\subsection{Texture Realism Loss}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
	\end{center}
	\caption{
		The neural texture looks more realistic with texture realism loss enabled.
	}
	\label{fig:texture_realism_ablation}
\end{figure}

These images could be regularized so that they're the same every time.

To do this we put a penalty on the latent texture that makes it $\pi$ look like its translation $\hat{p}$.

We use L2 and MSSSIM losses to do this.

This helps improve the translations.

There's a good reason for this: it's almost equivalent to unprojection consistency.
In fact, it can even be used on its own without unprojection consistency loss (both are sufficient to translate things.)

(Give theoretical explation)

There are some advantages over unprojection consistency though: 
smaller batch sizes (even a batch size of 1, which UC cant do),
you don't have to get lucky (the more chaotic, or even the more zoomed in a dataset becomes the less likely there is to be any collisions)

\subsection{Color Loss}
